---
title: "class11report for Divyanshu Kawankar"
output: github_document
---

First let's move the file

```{r}
Data_Export_Summary <- read.csv("Data Export Summary.csv")

DES <- Data_Export_Summary
```

```{r}
#Q1: What percentage of structures in the PDB are solved by X-Ray and Electron Microscopy?
## X-Ray - 87.5%
## Electron Microscopy - 4.95%

round(sum(DES$X.ray)/sum(DES$Total)*100,2)

round(sum(DES$EM)/sum(DES$Total)*100,2)

#Q2: What proportion of structures in the PDB are protein?
##87.35%

round(DES$Total[1]/sum(DES$Total)*100,2)

#Q3: Type HIV in the PDB website search box on the home page and determine how many HIV-1 protease structures are in the current PDB?
##99

#Q4: Water molecules normally have 3 atoms. Why do we see just one atom per water molecule in this structure?
##what we see is not the atom, but the whole molecule of water. Hydrogen is just too small proportionately which makes it impossible to see.

#Q5: There is a conserved water molecule in the binding site. Can you identify this water molecule? What residue number does this water molecule have (see note below)?
## Its residue number is 308:0

#Q6
##Dimers often have a bridge connecting the mirrored chains that monomers don't have. 
```

#Introduction to Bio3D in R

Read PDB file data into R
```{r}
library(bio3d)

pdb <- read.pdb("1hsg")

pdb

#Q7: How many amino acid residues are there in this pdb object? 
##198

#Q8: Name one of the two non-protein residues?
##HOH and MK1

#Q9: How many protein chains are in this structure?
## 2 Chainz
```

We can also find attributes of any obect using the following

```{r}
attributes(pdb)

head(pdb$atom)
```

#Comparative structure analysis of Adenylate Kinase

First install the packages for todays session

```{r}
#Q10. Which of the packages above is found only on BioConductor and not CRAN?
##msa

#Q11. Which of the above packages is not found on BioConductor or CRAN?
##devtools::install_bitbucket("Grantlab/bio3d-view")

#Q12. True or False? Functions from the devtools package can be used to install packages from GitHub and BitBucket?
##True
```

Search and retrieve ADK structures

```{r}
library(bio3d)
aa <- get.seq("1ake_A")

aa

#Q13. How many amino acids are in this sequence, i.e. how long is this sequence?
##214
```

Now, we can blast search the results to find similar sequences and structures. Plot a summary of the results

```{r}
b <- blast.pdb(aa)

hits <- plot(b)
```

List out the top hits

```{r}
head(hits$pdb.id)
```

Download related pdb files

```{r}
files <- get.pdb(hits$pdb.id, path="pdbs", split=TRUE, gzip=TRUE)
```

Align and Superpose structures

```{r}
# Code in error so I am submitting without muscle programming first
#pdbs <- pdbaln(files, fit = TRUE)#, exefile="msa")
```
```{r}
# ids <- basename.pdb(pdbs$id)

# plot(pdbs, labels=ids)
```


#Normal Mode Analysis

```{r}
#modes <- nma(pdbs)
```
```{r}
#Q14. What do you note about this plot? Are the black and colored lines similar or different? Where do you think they differ most and why?
## Based on the plot in the figure on the lab worksheet. It differs the most around residue number 125 because that is where the fluctuation is the greatest.
```

